Point estimates comparison for the simplified Naomi model

### 2023-07-14 src/naomi-simple_point-estimates/point-estimates.Rmd
Create point estimate plots of output split by parameter

>>>>

Version split by output type:

```{r}
df_metrics_output_split <- df_plot_output %>%
  group_by(method, indicator, type, par) %>%
  summarise(
    rmse = sqrt(mean((truth - approximate)^2)),
    mae = mean(abs(truth - approximate))
  ) %>%
  ungroup()

df_metrics_output_split_pct <- df_metrics_output_split %>%
  split(~ indicator + type + par) %>%
  lapply(function(x) {
    x %>% summarise(
      rmse_diff = 100 * diff(rmse) / max(rmse),
      mae_diff = 100 * diff(mae) / max(mae)
    )
  }) %>%
  bind_rows(.id = "id") %>%
  separate(id, c("indicator", "type", "par"), sep = "\\.")

df_metrics_output_split <- df_metrics_output_split %>%
  left_join(
    df_metrics_output_split_pct,
    by = c("indicator", "type", "par")
  ) %>%
  mutate(
    label = ifelse(
      method == "PCA-AGHQ",
      paste0("RMSE: ", signif(rmse, 2), " (", signif(rmse_diff, 2), "%)", "\nMAE: ", signif(mae, 2), " (", signif(mae_diff, 2), "%)"),
      paste0("RMSE: ", signif(rmse, 2), "\nMAE: ", signif(mae, 2))
    )
  )

plot_outputs <- function(.indicator, .par, col) {
  df_plot_output %>%
  filter(indicator == .indicator, par == .par) %>%
  ggplot() +
  geom_jitter(aes(x = truth, y = approximate - truth, color = par), shape = 1, alpha = 0.4, width = jitter_amount, height = jitter_amount) +
  scale_color_manual(values = c(col, "white", "white")) +
  facet_grid(indicator + par ~ method) +
  geom_abline(slope = 0, intercept = 0, linetype = "dashed", size = 0.25) +
  geom_text(
    data = filter(df_metrics_output_split, indicator == .indicator, par == .par),
    aes(x = -Inf, y = Inf, label = label), size = 3, hjust = 0, vjust = 1.5
  ) +
  labs(x = "NUTS", y = "Approximation - NUTS", col = "Output") +
  theme_minimal() +
  theme(legend.position = "none")
}

plot_outputs(.indicator = "Posterior mean estimate", .par = "rho_t1_out", col = "#E69F00")
plot_outputs(.indicator = "Posterior mean estimate", .par = "lambda_t1_out", col = "#009E73")
plot_outputs(.indicator = "Posterior mean estimate", .par = "alpha_t1_out", col = "#56B4E9")
plot_outputs(.indicator = "Posterior SD estimate", .par = "rho_t1_out", col = "#E69F00")
plot_outputs(.indicator = "Posterior SD estimate", .par = "lambda_t1_out", col = "#009E73")
plot_outputs(.indicator = "Posterior SD estimate", .par = "alpha_t1_out", col = "#56B4E9")
```
